ASYMPTOTIC VALIDITY OF THE BAYES-INSPIRED INDIFFERENCE ZONE PROCEDURE:

### 2015-06-18 paper/wish/wsc15paper.tex
new changes

\citeN{Frazier:BIZ} presents a new sequential elimination
IZ procedure, called BIZ (Bayes-inspired Indifference Zone), 
that eliminates the use of Bonferroni's inequality, reducing conservatism. 
This procedure's lower bound on worst-case probability of correct selection in the
preference zone is tight in continuous time, and almost tight in the
discrete time. In numerical experiments, the number of samples required
by BIZ is significantly smaller than that of procedures like the KN procedure of \citeN{Kim:2001} and
the $\mathcal{P}_{B}^{*}$ procedure of \citeN{Bechhofer:1968}, 
especially on problems with many alternatives. Unfortunately, the
proof from \cite{Frazier:BIZ} that the BIZ procedure satisfies the IZ guarantee for the discrete-time case assumes that (1) samples are normally distributed; 
(2) variances are known;
and (3) the variances are either common across alternatives, or have an unrealistic integer multiple structure.

@@

In the Indifference-Zone Ranking and Selection, the procedure is indifferent
in the selection of a system whenever the means of the populations
are nearly the same. Formally, let $\mu=\left[\mu_{k},\ldots,\mu_{1}\right]$
be the vector of the true means, the \emph{indifference zone} is defined
as the set $\left\{ \mu\in\mathbb{R}^{k}:\mu_{\left[k\right]}-\mu_{\left[k-1\right]}<\delta\right\} $.
The complement of the indifference zone is called the \emph{preference
zone} (PZ) and $\delta>0$ is called the indifference zone parameter.
We say that a procedure meets the \emph{indifference-zone (IZ) guarantee
}at $P^{*}\in\left(1/k,1\right)$ and $\delta>0$ if
\[
\mbox{PCS}\left(\mu\right)\geq P^{*}\mbox{ for all }\mu\in\mbox{PZ}\left(\delta\right).
\]
We assume $P^{*}>1/k$ because IZ guarantees can be meet by choosing
$\hat{x}$ uniformly at random from among $\left\{ 1,\ldots,k\right\} $.

@@

BIZ is an elimination procedure. This procedure maintains a set of
alternatives that are candidates for the best system, and it takes samples from each
alternative in this set at each point in time. At beginning, all alternatives
are possible candidates for the best system, and over the time alternatives are eliminated.
The procedure ends when there is only one alternative in the contention
set and this remain alternative is chosen as the best.

@@

A slight modification of the discrete-time BIZ procedure for unknown and/or heterogeneous sampling
variances is given below.  It takes a variable number of samples
from each alternative, and $n_{tx}$ is this number. This algorithm
depends on a collection of integers $B_{1},\ldots,B_{k}$, $P^{*},c,\delta$
and $n_{0}$. Here, $n_{0}$ is the number of samples to use in the first
stage of samples, and $100$ is the recommended value for $n_{0}$. The paramater
$B_{x}$ controls the number of samples taken from system $x$ in
each stage. To simplify our analysis, the procedure presented is a slight modification of the original BIZ 
procedure \cite{Frazier:BIZ} where $z \in \mbox{arg max}_{x\in A} \lambda^2_{x}$, instead 
of $z \in \mbox{arg min}_{x\in A} n_{tx} / \lambda^2_{x}$. According to numerical experiments on common cases, there is little difference in the PCS between the version of BIZ
we analyze and the version in \citeN{Frazier:BIZ}.

For each $t$, $x\in\left\{ 1,\ldots,k\right\} $, and subset $A\subset\left\{ 1,\ldots,k\right\} $,
we define a function
\[
q'_{tx}\left(A\right)=\mbox{exp}\left(\delta\beta_{t}\frac{Z_{tx}}{n_{tx}}\right)\left/\sum_{x'\in A}\mbox{exp}\left(\delta\beta_{t}\frac{Z_{tx'}}{n_{tx'}}\right),\right.\mbox{ }\beta_{t}=\frac{\sum_{x'\in A}n_{tx'}}{\sum_{x'\in A}\hat{\lambda}_{tx'}^{2}}
\]
where $\hat{\lambda}_{tx'}^{2}$ is the sample variance of all samples
from alternative $x$ thus far and $Z_{tx}=Y_{n_{tx},x}$.

@@

In this section we prove that the BIZ procedure satisfies asymptotically the IZ guarantee
when the variances are known. This means that we consider a collection of
ranking and selection problems parametrized by $\delta>0$.  
For the problem given $\delta$, we suppose that the vector of the true means
$\mu=\left[\mu_{k},\ldots,\mu_{1}\right]$ is equal to $\delta a$ for some fixed $a\in\mathbb{R}^{k}$ that
does not depend on $\delta$ and $a_{k}>a_{k-1}\geq \cdots \geq a_{1}$, $a_{k}-a_{k-1}>1$.
Moreover, the variances of the alternatives are finite, strictly greater than zero and do not depend on $\delta$.
We also suppose that samples from system $x\in\left\{ 1\ldots,k\right\} $ are identically distributed
and independent, over time and across alternatives. We also define
$\lambda_{z}^{2}:=\max_{i\in\left\{ 1\ldots,k\right\} }\lambda_{i}^{2}$.

@@

The first is the mapping from the raw discrete-time random walk $\left(Y_{tx}:t\in\mathbb{N},x\in\left\{ 1,\ldots,k\right\} \right)$
onto a time changed version of this random walk, written as $\left(Z_{tx}:t\in\mathbb{N},x\in\left\{ 1,\ldots,k\right\} \right)$,
where we recall $Z_{tx}=Y_{n_{x}\left(t\right),t}$ is the sum of
the samples from alternative $x$ observed by stage $t$.

The second maps this time-changed random walk through a non-linear
mapping for each $t,x$ and subset $A\subset\left\{ 1,\ldots,k\right\} $,
to obtain $\left(q_{tx}^{'}\left(A\right):t\in\mathbb{N},A\subset\left\{ 1,\ldots,k\right\} ,x\in A\right)$,
where

@@

We have proved the asymptotic validity of the Bayes-inspired Zone
procedure \cite{Frazier:BIZ} when the variances are known.
This algorithm takes fewer samples than other IZ procedures, especially for
problems with large numbers of alternatives, and so characterizing when it
satisfies the indifference-zone guarantee is important for understanding when
it should be used in practice.

>>>>

\citeN{Frazier:BIZ} presents a new sequential elimination
IZ procedure, called BIZ (Bayes-inspired Indifference Zone), 
that eliminates the use of Bonferroni's inequality, reducing conservatism. 
This procedure's lower bound on the worst-case probability of correct selection in the
preference zone is tight in continuous time, and almost tight in discrete time. In numerical experiments, the number of samples required
by BIZ is significantly smaller than that of procedures like the $\mathcal{P}_{B}^{*}$ procedure of \citeN{Bechhofer:1968} and the KN procedure of \citeN{Kim:2001}, especially on problems with many alternatives. Unfortunately, the
proof from \cite{Frazier:BIZ} that the BIZ procedure satisfies the IZ guarantee for the discrete-time case assumes that (1) samples are normally distributed; 
(2) variances are known;
and (3) the variances are either common across alternatives, or have an unrealistic integer multiple structure.

@@

In the Indifference-Zone Ranking and Selection, the procedure is indifferent
in the selection of a system whenever the means of the populations
are nearly the same. Formally, let $\mu=\left[\mu_{1},\ldots,\mu_{k}\right]$
be the vector of the true means, the \emph{indifference zone} is defined
as the set $\left\{ \mu\in\mathbb{R}^{k}:\mu_{\left[k\right]}-\mu_{\left[k-1\right]}<\delta\right\} $.
The complement of the indifference zone is called the \emph{preference
zone} (PZ) and $\delta>0$ is called the indifference zone parameter.
We say that a procedure meets the \emph{indifference-zone (IZ) guarantee
}at $P^{*}\in\left(1/k,1\right)$ and $\delta>0$ if
\[
\mbox{PCS}\left(\mu\right)\geq P^{*}\mbox{ for all }\mu\in\mbox{PZ}\left(\delta\right).
\]
We assume $P^{*}>1/k$ because IZ guarantees can be meet by choosing
$\hat{x}$ uniformly at random from $\left\{ 1,\ldots,k\right\} $.

@@

BIZ is an elimination procedure. This procedure maintains a set of
alternatives that are candidates for the best system, and it takes samples from each
alternative in this set at each point in time. At beginning, all alternatives
are possible candidates for the best system, and over the time alternatives are eliminated.
The procedure ends when there is only one alternative in the contention
set and this remaining alternative is chosen as the best.

@@

A slight modification of the discrete-time BIZ procedure for unknown and/or heterogeneous sampling
variances is given below.  This algorithm takes a variable number of samples
from alternative $x$ at time $t$, and $n_{tx}$ is this number (its definition may found in the algorithm given below). 
This algorithm depends on a collection of integers $B_{1},\ldots,B_{k}$, $P^{*},c,\delta$
and $n_{0}$. Here, $n_{0}$ is the number of samples to use in the first
stage of samples, and $100$ is the recommended value for $n_{0}$ when the variances are unknown. The paramater
$B_{x}$ controls the number of samples taken from system $x$ in
each stage. To simplify our analysis, the procedure presented is a slight modification of the original BIZ 
procedure \cite{Frazier:BIZ} where $z \in \mbox{arg max}_{x\in A} \lambda^2_{x}$, instead 
of $z \in \mbox{arg min}_{x\in A} n_{tx} / \lambda^2_{x}$. According to numerical experiments on common cases, there is little difference in the PCS between the version of BIZ
we analyze and the version in \citeN{Frazier:BIZ}.

For each $t$, $x\in\left\{ 1,\ldots,k\right\} $, and subset $A\subset\left\{ 1,\ldots,k\right\} $,
we define a function
\[
q'_{tx}\left(A\right)=\mbox{exp}\left(\delta\beta_{t}\frac{Z_{tx}}{n_{tx}}\right)\left/\sum_{x'\in A}\mbox{exp}\left(\delta\beta_{t}\frac{Z_{tx'}}{n_{tx'}}\right),\right.\mbox{ }\beta_{t}=\frac{\sum_{x'\in A}n_{tx'}}{\sum_{x'\in A}\hat{\lambda}_{tx'}^{2}}
\]
where $\hat{\lambda}_{tx'}^{2}$ is the sample variance of all samples
from alternative $x$ thus far, and $Z_{tx}=Y_{n_{tx},x}$ is the sum of
the samples from alternative $x$ observed by stage $t$.

@@

In this section we prove that the BIZ procedure satisfies asymptotically the IZ guarantee
when the variances are known. This means that we consider a collection of
ranking and selection problems parametrized by $\delta>0$.  
For the problem given $\delta$, we suppose that the vector of the true means
$\mu=\left[\mu_{1},\ldots,\mu_{k}\right]$ is equal to $\delta a$ for some fixed $a\in\mathbb{R}^{k}$ that
does not depend on $\delta$ and $a_{k}>a_{k-1}\geq \cdots \geq a_{1}$, $a_{k}-a_{k-1}>1$.
Moreover, the variances of the alternatives are finite, strictly greater than zero and do not depend on $\delta$.
We also suppose that samples from system $x\in\left\{ 1\ldots,k\right\} $ are identically distributed
and independent, over time and across alternatives. We also define
$\lambda_{z}^{2}:=\max_{i\in\left\{ 1\ldots,k\right\} }\lambda_{i}^{2}$.

@@

The first mapping is from the raw discrete-time random walk $\left(Y_{tx}:t\in\mathbb{N},x\in\left\{ 1,\ldots,k\right\} \right)$
onto a time changed version of this random walk, written as $\left(Z_{tx}:t\in\mathbb{N},x\in\left\{ 1,\ldots,k\right\} \right)$,
where we recall $Z_{tx}=Y_{n_{tx},x}$ is the sum of
the samples from alternative $x$ observed by stage $t$.

The second one maps this time-changed random walk through a non-linear
mapping for each $t,x$ and subset $A\subset\left\{ 1,\ldots,k\right\} $,
to obtain $\left(q_{tx}^{'}\left(A\right):t\in\mathbb{N},A\subset\left\{ 1,\ldots,k\right\} ,x\in A\right)$,
where

@@

We have proved the asymptotic validity of the Bayes-inspired Indifference Zone
procedure \cite{Frazier:BIZ} when the variances are known.
This algorithm takes fewer samples than other IZ procedures, especially for
problems with large numbers of alternatives, and so characterizing when it
satisfies the indifference-zone guarantee is important for understanding when
it should be used in practice.
